Backscatter Modulation Design for Symbiotic Radio Networks

### 2021-09-07 main.tex
:pencil: Formulate WSR problem

	\begin{section}{System Model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{symbiotic_radio.pdf_tex}
			\caption{A single-user single-tag symbiotic radio system.}
			\label{fi:symbiotic_radio}
		\end{figure}
		As shown in Fig.~\ref{fi:symbiotic_radio}, we propose a single-user (UE) single-tag (TG) symbiotic radio network where the RF signal generated by the single-antenna Access Point (AP) is shared by two coexisting systems. In the primary AP-UE downlink system, the AP transmits to the single-antenna user. In the secondary AP-TG-UE backscatter system, the AP acts as the carrier emitter, the user serves as the backscatter reader, and the single-antenna tag modulates its information over the reradiated RF signal by varying the reflection coefficient. Denote the AP-UE direct channel as $h_{\mathrm{D}}$, the AP-TG forward channel as $h_{\mathrm{F}}$, and the TG-UE backward channel as $h_{\mathrm{B}}$. We consider the quasi-static block fading model and assume the CSI of the direct channel and the cascaded forward-backward channel $h_{\mathrm{C}} \triangleq h_{\mathrm{B}} h_{\mathrm{F}}$ are known at the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient CSI acquisition at the AP can be challenging. One possible approach is that the AP sends known pilots, the tag responds in a pre-defined manner, and the user performs least-square estimation then feeds back to the AP \cite{Bharadia2015,Yang2015b,Guo2019e}.} It is assumed that the primary symbol $s$ follows standard CSCG distribution $\mathcal{CN}(0,1)$ and the secondary symbol $c$ employs $M$-PSK modulation by \eqref{eq:backscatter_modulation}. Due to the practical constraints on switching speed and synchronization gap, the passive tag typically transmits at a much lower data rate than the AP. Hence, we assume the secondary symbol period is $N \gg 1 \in \mathbb{Z}_{++}$ times the primary symbol period and focus on the interval of one particular $c$. At (primary) symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, the user simultaneously captures the signal from both primary and secondary links as\footnote{We assume the time difference of arrival from the AP-UE path and the AP-TG-UE path are negligible compared to the symbol period \cite{Guo2019b,Liang2020,Long2020a}.}
		\begin{equation}
			y[n] = \sqrt{p} h_{\mathrm{D}} s[n] + \sqrt{\alpha p} h_{\mathrm{C}} c s[n] + w[n],
		\end{equation}
		where $p$ is the average transmit power at the AP and $w \sim \mathcal{CN}(0,\sigma^2)$ is the additive white Gaussian noise. We also define $\boldsymbol{y} \triangleq \bigl[y[1], \ldots, y[N]\bigr]^T$.

@@

		\begin{remark}
			The main difference between symbiotic radio and conventional MAC is that the primary message also reaches the user from the backscatter link. This characteristic inspires one to first decode the tag message, then model its contribution within the equivalent channel during primary decoding (i.e., unify secondary decoding and backscatter channel training), instead of performing SIC. In such case, for each fading block, the primary transmission is able to achieve ergodic capacity with artificial channel variation created by the backscatter modulation.
		\end{remark}

		To investigate how backscatter modulation potentially benefits the primary transmission, we first decode the tag symbol $c$ in presence of unknown AP symbol $\boldsymbol{s}$. Interestingly, the tag detection indeed coincides with Ambient Backscatter Communications (AmBC) where the signal from the ambient source is unknown. Denote $\mathcal{H}_m$ as the hypothesis that the tag transmits $c_m$. In such case, the received signal per symbol block follows the CSCG distribution of $y_m[n] \sim \mathcal{CN}(0,\sigma_m^2)$, where
			\sigma_m^2 \triangleq \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_m \rvert^2 p + \sigma^2
		can be estimated at the user. For the ease of exposition, we sort $\{\sigma_m^2\}$ in a descending order by bijective mapping $f \colon m \mapsto i$,\footnote{Note that the mapping is not unique and the detection fails when two different constellation points yield the same energy level.} and formulate a sequence $\langle \sigma_i^2 \rangle$ where $\sigma_i^2 \ge \sigma_j^2$ for $i > j$, $i,j \in \mathcal{M}$. Following \cite{Qian2019}, the optimal Maximum-Likelihood (ML) detector boils down to the energy detector, and the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is
			\Lambda_{i, j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{(\sigma_i^2 - \sigma_j^2) z}{\sigma_i^2 \sigma_j^2} \right),
		where $f(\boldsymbol{y} \mid \mathcal{H}_i)$, $f(\boldsymbol{y} \mid \mathcal{H}_j)$ denote respectively the conditional probability density function of receiving $\boldsymbol{y}$ under hypothesis $\mathcal{H}_i$ and $\mathcal{H}_j$, and $z \triangleq \lVert y \rVert^2$ is the received signal energy over $N$ symbol blocks. The corresponding decision rule is
			\Lambda_{i, j}(\boldsymbol{y}) \underset{H_j}{\overset{H_i}{\gtrless}} 1 \iff z \underset{H_j}{\overset{H_i}{\gtrless}} T_{i, j},
		where the optimal detection threshold is
			T_{i, j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2}.
		On top of this, the decision region of hypothesis $\mathcal{H}_i$ can be expressed as
		% \begin{equation}
		% 	\mathcal{R}(\mathcal{H}_i) \triangleq
		% 	\begin{cases}
		% 		[0, T_{1, 2}), & i = 1, \\
		% 		[T_{M-1, M}, \infty), & i = M, \\
		% 		[T_{i-1, i}, T_{i, i+1}), & \text{otherwise}
		% 	\end{cases}
		% \end{equation}
			\mathcal{R}_i \triangleq [T_{i-1, i}, T_{i, i+1}),
		where we define $T_{0, 1} \triangleq 0$ and $T_{M, M+1} \triangleq \infty$. On the other hand, the transition probability matrix is
			\boldsymbol{P} =
			\begin{bmatrix}
				p_{1 \mid 1} & \ldots & p_{M \mid 1} \\
				\vdots & \ddots & \vdots \\
				p_{1 \mid M} & \ldots & p_{M \mid M}
			\end{bmatrix},
		where $p_{j \mid i}$ denotes the transition probability from channel input state $i$ to output state $j$. It can be derived as
			p_{j \mid i} = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z
			\label{eq:transition_probability}
		where $f(z \mid \mathcal{H}_i)$ is the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$. Since $z$ follows chi-squared distribution with $2N$ degrees of freedom, it holds that
			f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} \Gamma(N)}
			\label{eq:conditional_pdf}
		where $\Gamma(\cdot)$ is the gamma function and $\Gamma(N) = (N - 1) !$ for positive integer $N$. Therefore, the transition matrix $\boldsymbol{P}$ can be calculated by substituting \eqref{eq:conditional_pdf} into \eqref{eq:transition_probability}, and the optimal input distribution can be obtained by the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972}.

		% During the backscatter detection, the conditional probability density function of the channel output given the tag input for $M$-PSK is
		% \begin{equation}
		% 	f_{Y \mid C}(y \mid c_m) = ?
		% \end{equation}

		% Since $\mathbb{E}[\lvert s \rvert^2] = \mathbb{E}[\lvert c \rvert^2] = 1$, by treating the primary interference as noise, the SINR for the user to decode tag message $c$ is
		% \begin{equation}
		% 	\gamma_c = \frac{\alpha p \lvert h_{\mathrm{C}} \rvert^2}{p \lvert h_{\mathrm{D}} \rvert^2 + 1}.
		% \end{equation}
		Once the tag message is successfully recovered, we combine the backscattered symbol with the cascaded channel to eliminate the uncertainty of the AP-TG-UE path, and the received signal is essentially
		\begin{equation}
			y[n] = \sqrt{p} (h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c) s[n] + w[n] \triangleq \sqrt{p} h(c) s + w[n],
		\end{equation}
		which is reminiscent of IRS-aided point-to-point transmission with the equivalent channel defined as
		\begin{equation}
			h(c) \triangleq h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c.
		\end{equation}
		That is to say, the passive tag not only embeds its own message in the reflection pattern, but also influences the legacy transmission. For primary transmission, backscatter modulation creates a fast fading channel within the coherence time, and the equivalent CSI is known at the receiver once the backscattered symbol is successfully decoded. Therefore, the ergodic capacity of primary transmission within each fading block is \cite{Tse2005}
		\begin{equation}
			R_s = \mathbb{E}_c \bigl[ \log_2 ( 1 + \lvert h(c) \rvert^2 ) \bigr].
		\end{equation}
		We aims to optimize the input distribution of $c$ (i.e., the probability mass function of $M$-PSK) to achieve a flexible balance between the primary and secondary links.

		% channel training - backscatter decoding

		% \begin{remark}
		% 	To investigate how backscatter modulation potentially benefits the primary transmission, we instead decode the secondary link before the primary link. Once the tag message is successfully decoded, the uncertainty of the AP-TG-UE path can be perfectly removed (by combining the backscattered symbol and the cascaded channel), and its contribution can be modeled within the equivalent AP-UE channel. This is reminiscent of IRS-aided point-to-point transmission with CSI uncertainty (by backscatter modulation instead of channel estimation), where the passive tag simultaneously embeds its own message (embodied in secondary decoding) and assists the legacy transmission (embodied in primary decoding).

		% 	[Channel over channel, randomness over randomness]
		% \end{remark}

		% Define $s_k$ as the primary symbol for user $k$ with $\boldsymbol{s} \triangleq [s_1,\ldots,s_K]^H \in \mathbb{C}^{K \times 1}$ satisfying $\mathbb{E}\{\boldsymbol{s}\boldsymbol{s}^H\}=\boldsymbol{I}$, and $c_{l_k}$ as the secondary symbol of tag $l_k$ with $\boldsymbol{c}_k \triangleq [c_1,\ldots,c_{L_k}]^H \in \mathbb{C}^{L_k \times 1}$ satisfying $\mathbb{E}\{\boldsymbol{c}_k\boldsymbol{c}_k^H\}=\boldsymbol{I}$. Let $s_k \sim \mathcal{CN} (0,1)$ and $c_{l_k}$ employs $M$-PSK by \eqref{eq:reflection_coefficient}. As tags typically transmit at a much lower rate than the AP, we assume the secondary symbol period $T_c$ is $N \in \mathbb{Z}_{++}$ times the primary symbol period $T_s$ (i.e., $T_c=NT_s$) and focus on one particular secondary symbol period. For linear precoding with no dedicated tag beams, the transmit signal during the primary symbol period $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
		% \begin{equation}
		% 	\boldsymbol{x}(n) = \sum_{k=1}^K \boldsymbol{w}_k s_k(n),
		% \end{equation}
		% where $\boldsymbol{w}_k$ is the precoder for user $k$ satisfying the average transmit power constraint $\sum_{k=1}^K \lVert \boldsymbol{w}_k \rVert^2 \le P$. The received signal at tag $l_k$ is\footnote{For simplicity, the backscattered signals from all other tags are modeled within noise.}
		% \begin{equation}
		% 	y_{l_k}(n) = \sum_{j=1}^K \boldsymbol{h}_{\mathrm{F},l_k}^H \boldsymbol{w}_j s_j(n) + z_{l_k}(n),
		% \end{equation}
		% where $z_{l_k} \sim \mathcal{CN} (0,\sigma_{l_k}^2)$ is the additive white Gaussian noise\footnote{Since the tag employs no active RF components, the noise captured at backscatter antenna $z_{l_k}$ is assumed negligible \cite{Nikitin2005,Arnitz2013,Wu2021b}.}. Hence, the corresponding antenna input power is
		% \begin{equation}
		% 	P_{0,l_k} = \sum_{j=1}^K \lvert \boldsymbol{h}_{\mathrm{F},l_k}^H \boldsymbol{w}_j \rvert^2.
		% 	\label{eq:P_0}
		% \end{equation}
		% In practice, the rectifier is a non-linear device and the RF-to-DC conversion efficiency depends on the input power \cite{Clerckx2016a,Clerckx2018,Clerckx2019}. On top of \eqref{eq:P_H} and \eqref{eq:P_0}, when all modulation states are equiprobable, the average harvester output power is
		% \begin{align}
		% 	P_{l_k}
		% 	& = \frac{1}{M} \Biggl( \sum_{i_1} \zeta \biggl( \eta_{i_1} (1 - \alpha_{l_k}^2) \sum_{j=1}^K \lvert \boldsymbol{h}_{\mathrm{F},l_k}^H \boldsymbol{w}_j \rvert^2 \biggr) \\
		% 	& \quad + \sum_{i_2} \zeta \biggl( \frac{(1 - \alpha_{l_k}^2) \sum_{j=1}^K \lvert \boldsymbol{h}_{\mathrm{F},l_k}^H \boldsymbol{w}_j \rvert^2}{\eta_{i_2}} \biggr) \Biggr),
		% \end{align}
		% where $i_1 \ge M {\arccos \alpha_{l_k}} / {2 \pi}$, $i_2<M {\arccos \alpha_{l_k}} / {2 \pi}$, and $\zeta(\cdot)$ is the harvester response function. On the other hand, we define the scattered channel by tag $l_k$ as
		% \begin{equation}
		% 	\boldsymbol{h}_{l_k}^H \triangleq \alpha_{l_k} h_{\mathrm{B},l_k} \boldsymbol{h}_{\mathrm{F},l_k}^H.
		% \end{equation}
		% Hence, the received signal at user $k$ is
		% \begin{align}
		% 	y_k(n)
		% 	& = \sum_{j=1}^K \left( \boldsymbol{h}_{\mathrm{D},k}^H + \sum_{l_k=1}^{L_k} c_{l_k} \boldsymbol{h}_{l_k}^H \right) \boldsymbol{w}_j s_j(n) + z_k(n) \\
		% 	& \triangleq \sum_{j=1}^K \boldsymbol{h}_k^H \boldsymbol{w}_j s_j(n) + z_k(n),
		% \end{align}
		% where
		% \begin{equation}
		% 	\boldsymbol{h}_k^H \triangleq \boldsymbol{h}_{\mathrm{D},k}^H + \sum_{l_k=1}^{L_k} c_{l_k} \boldsymbol{h}_{l_k}^H
		% 	\label{eq:h}
		% \end{equation}
		% is the equivalent channel of user $k$ and $z_k \sim \mathcal{CN} (0,\sigma_k^2)$ is the additive white Gaussian noise.
		% \begin{remark}
		% 	From the perspective of broadcast, the components scattered by the tags essentially create uncertainty over the direct AP-UE channel. If the backscattered symbols are unknown when decoding the broadcasted symbols, the uncertainty should be either covered by non-coherent detection \cite{Long2020a} or modeled as CSI error that introduces interference. That is to say, the equivalent channel is perfectly known only when all tag massages are successfully decoded.
		% \end{remark}

		% \begin{figure}[!t]
		% 	\centering
		% 		\resizebox{0.95\columnwidth}{!}{
		% 			\begin{tikzpicture}
		% 				\foreach \x in {1,...,12}
		% 					\draw [pattern=crosshatch dots,pattern color=blue](\x,0) rectangle ++(1,1);
		% 				\foreach \x in {1,...,12}
		% 					\foreach \y in {-3,...,-1}{
		% 						\pgfmathsetmacro\floorval{int(floor((\x+\y)/4))}
		% 						\pgfmathsetmacro\modval{int(mod((\x+\y),4))}
		% 						\ifnum \floorval=0
		% 							\ifnum \modval=0
		% 								\draw [pattern=horizontal lines,pattern color=red](\x,\y) rectangle ++(1,1);
		% 							\else
		% 								\draw [pattern=horizontal lines,pattern color=yellow](\x,\y) rectangle ++(1,1);
		% 							\fi
		% 						\else
		% 							\ifnum \floorval=1
		% 								\ifnum \modval=0
		% 									\draw [pattern=north west lines,pattern color=red](\x,\y) rectangle ++(1,1);
		% 								\else
		% 									\draw [pattern=north west lines,pattern color=yellow](\x,\y) rectangle ++(1,1);
		% 								\fi
		% 							\else
		% 								\ifnum \floorval=2
		% 									\ifnum \modval=0
		% 										\draw [pattern=vertical lines,pattern color=red](\x,\y) rectangle ++(1,1);
		% 									\else
		% 										\draw [pattern=vertical lines,pattern color=yellow](\x,\y) rectangle ++(1,1);
		% 									\fi
		% 								\else
		% 									\draw (\x,\y) rectangle ++(1,1);
		% 									% \ifnum \modval=0
		% 									% 	\draw (\x,\y) rectangle ++(1,1);
		% 									% \else
		% 									% 	\draw [pattern=north east lines,pattern color=yellow](\x,\y) rectangle ++(1,1);
		% 									% \fi
		% 								\fi
		% 							\fi
		% 						\fi
		% 					}
		% 				\node[font=\huge] at (-2,0.5) {Broadcast};
		% 				\node[font=\huge] at (-2,-0.5) {Tag \num{1}};
		% 				\node[font=\huge] at (-2,-1.5) {Tag \num{2}};
		% 				\node[font=\huge] at (-2,-2.5) {Tag \num{3}};
		% 				\node[font=\huge] at (14,-1) {$\cdots$};
		% 				\node[font=\huge,right] at (16.75,0){$b=1$};
		% 				\node[font=\huge,right] at (16.75,-1){$b=2$};
		% 				\node[font=\huge,right] at (16.75,-2){$b=3$};
		% 				\draw [pattern=horizontal lines](16,-0.25) rectangle ++(0.5,0.5);
		% 				\draw [pattern=north west lines](16,-1.25) rectangle ++(0.5,0.5);
		% 				\draw [pattern=vertical lines](16,-2.25) rectangle ++(0.5,0.5);
		% 				\draw[<->] (1,1.5) -- (2,1.5) node[font=\huge,midway,above]{$T_s$};
		% 				\draw[<->] (1,-3.5) -- (5,-3.5) node[font=\huge,midway,below=0.125]{$T_c=NT_s$};
		% 				\draw[->] (10.5,1.625) -- (10.5,1.25) node[font=\huge,at start,above]{Block $r$};
		% 			\end{tikzpicture}
		% 		}
		% 	\caption{Primary and secondary symbol blocks received by user $k$ for $N=4$ and $L_k=3$. The blocks are normalized to the primary symbol period $T_s$. In the broadcast link, each block contains the message of all users at a specific time. In the backscatter links, each tag symbol lasts $N$ blocks (illustrated by a specific pattern) and the tag streams are delayed by multiples of $T_s$. Apart from decoding the self message, each user also decodes at most one tag message per primary symbol period (denoted by red blocks) and regards it as part of known channel in the following $N-1$ blocks.}
		% 	\label{fi:blocks}
		% \end{figure}

		% To mitigate the interference from the backscatter link, we utilize its low rate property and propose a joint user and tag multiple access scheme as illustrated in Fig.~\ref{fi:blocks}. Specifically, the broadcast system can employ any general multiple access scheme\footnote{Since tags are associated to the nearest user, non-orthogonal protocols (e.g., NOMA and MU-LP) involving less coordination among users and tags are preferred \cite{Ding2021}.} (denoted by blue blocks), while the backscatter system integrates TDMA and NOMA as follows. Assuming the number of tags associated to user $k$ satisfies $L_k \le N$, $\forall k \in \mathcal{K}$\footnote{The proposed scheme can be extended to case of $L_k > N$, where at most $\lceil L_k/N \rceil$ tags transmit synchronously and user $k$ decodes up to $\lceil L_k/N \rceil$ tags per primary symbol period. Here we assume $L_k \le N$ for simplicity.}, we intentionally delay the stream of tag $l_k$ by $l_k-1$ primary symbol periods such that all tags transmit asynchronously and non-orthogonally. In such case, each user only needs to decode at most one tag message per primary symbol period (denoted by red blocks) and models it as part of the estimated channel in the following $N-1$ primary symbol periods (denoted by yellow blocks). We denote $r \in \mathbb{Z}_{++}$ as the index of primary symbols, and define $b \triangleq \lceil r/N \rceil$ as the index of secondary symbols and $d \equiv r \pmod N$ as the remainder of $N$ divides $r$. Therefore, the backscattered symbol by tag $l_k$ at block $r$ can be related to its index $b$ as
		% \begin{equation}
		% 	c_{l_k}(r) =
		% 	\begin{cases}
		% 		c_{l_k}(b), & d = 0 \text{ or } d \ge l_k, \\
		% 		c_{l_k}(b-1), & 0 < d < l_k.
		% 	\end{cases}
		% \end{equation}
		% It is assumed that $c_{l_k}(0)$, $\forall l_k \in \mathcal{L}_k$ is known at user $k$ and can be designed as zeros or pilots or cyclic prefixes.

		% At block $r$, user $k$ always decodes its $r$-th primary symbol $s_k(r)$ first. If $d=0$ or $d>L_k$ \footnote{Note that $d=0$ corresponds to $n=N$.}, all backscattered symbols would be the same as in the previous block and no uncertainty is introduced by the backscattered link (denoted by all-yellow columns). Therefore, the equivalent channel at block $r$ is perfectly known and the tags create no interference to the primary transmission. On the other hand, if $0 < d \le L_k$, tag $d$ would trigger a new symbol $c_d(b)$ that lasts $N$ blocks but should be decoded within the current block $r$. In this case, user $k$ first treats the channel uncertainty from $c_d(b)$ as interference during primary decoding, then cancels the interference from decoded primary symbols and detects $c_d(b)$. Once a backscattered symbol is successfully decoded, its contribution to the equivalent channel \eqref{eq:h} is known. Therefore, under perfect detection, the estimated channel of user $k$ at block $r$ is
		% \begin{equation}
		% 	\bar{\boldsymbol{h}}_k^H(r) =
		% 		\begin{cases}
		% 			\boldsymbol{h}_{\mathrm{D},k}^H + \boldsymbol{c}_k^H(r) \boldsymbol{H}_k, & d = 0 \text{ or } d > L_k, \\
		% 			\boldsymbol{h}_{\mathrm{D},k}^H + \boldsymbol{c}_{k \setminus d}^H(r) \boldsymbol{H}_{k \setminus d}, & 0 < d \le L_k,
		% 		\end{cases}
		% 		\label{eq:h_bar}
		% \end{equation}
		% where we define $\boldsymbol{c}_{k \setminus d} \triangleq [c_1,\ldots,c_{d-1},c_{d+1},\ldots,c_{L_k}]^H \in \mathbb{C}^{(L_k-1) \times 1}$, $\boldsymbol{H}_k \triangleq [\boldsymbol{h}_1,\ldots,\boldsymbol{h}_{L_k}]^H \in \mathbb{C}^{L_k \times Q}$ and $\boldsymbol{H}_{k \setminus d} \triangleq [\boldsymbol{h}_1,\ldots,\boldsymbol{h}_{d-1},\boldsymbol{h}_{d+1},\ldots,\boldsymbol{h}_{L_k}]^H \in \mathbb{C}^{(L_k-1) \times Q}$. Besides, the corresponding channel uncertainty is
		% \begin{equation}
		% 	\tilde{\boldsymbol{h}}_k^H(r) = \boldsymbol{h}_k^H(r) - \bar{\boldsymbol{h}}_k^H(r) =
		% 		\begin{cases}
		% 			0, & d = 0 \text{ or } d > L_k, \\
		% 			c_{d}(r) \boldsymbol{h}_{d}^H, & 0 < d \le L_k.
		% 		\end{cases}
		% 		\label{eq:h_tilde}
		% \end{equation}
		% \begin{remark}
		% 	From the perspective of broadcast, the backscattered channel is similar to the auxiliary channel provided by IRS. Once a tag symbol is successfully decoded, the corresponding channel uncertainty can be mitigated in the following $N-1$ primary symbol periods. This decoding mechanism can be viewed as a backscatter channel training process where the cascaded channels remain unchanged and the tag reflection coefficients are learned. If $N \gg L_k$, the training overhead (corresponding to $0 < d \le L_k$) can be omitted where the tags backscatter at very low rates and behave similar to the IRS elements. That is to say, passive beamforming can be enabled by carefully choosing the backscatter symbols based on CSI.
		% \end{remark}

		% Next, we investigate the performance of the proposed protocol under typical primary multiple access schemes.

>>>>

	\begin{section}{System Model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{symbiotic_radio.pdf_tex}
			\caption{A single-user single-tag symbiotic radio system.}
			\label{fi:symbiotic_radio}
		\end{figure}
		As shown in Fig.~\ref{fi:symbiotic_radio}, we propose a single-user (UE) single-tag (TG) symbiotic radio network where the RF signal generated by the single-antenna Access Point (AP) is shared by two coexisting systems. In the primary AP-UE downlink system, the AP transmits to the single-antenna user. In the secondary AP-TG-UE backscatter system, the AP acts as the carrier emitter, the user serves as the backscatter reader, and the single-antenna tag modulates its information over the reradiated RF signal by varying the reflection coefficient. Denote the AP-UE direct channel as $h_{\mathrm{D}}$, the AP-TG forward channel as $h_{\mathrm{F}}$, and the TG-UE backward channel as $h_{\mathrm{B}}$. We consider the quasi-static block fading model and assume the CSI of the direct channel and the cascaded forward-backward channel $h_{\mathrm{C}} \triangleq h_{\mathrm{B}} h_{\mathrm{F}}$ are known at the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient CSI acquisition at the AP can be challenging. One possible approach is that the AP sends known pilots, the tag responds in a pre-defined manner, and the user performs least-square estimation then feeds back to the AP \cite{Bharadia2015,Yang2015b,Guo2019e}.} It is assumed that the primary symbol $s$ follows standard CSCG distribution $\mathcal{CN}(0,1)$ and the secondary symbol $c$ employs $M$-PSK modulation by \eqref{eq:backscatter_modulation}. Due to the practical constraints on switching speed and synchronization gap, the passive tag typically transmits at a much lower data rate than the AP. Hence, we assume the secondary symbol period is $N \gg 1 \in \mathbb{Z}_{++}$ times the primary symbol period and focus on the interval of one particular $c$. At (primary) symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, the user simultaneously captures the signal from both primary and secondary links as\footnote{We assume the time difference of arrival from the AP-UE path and the AP-TG-UE path are negligible compared to the symbol period \cite{Guo2019b,Liang2020,Long2020a}.}
		\begin{equation}
			y[n] = \sqrt{P} h_{\mathrm{D}} s[n] + \sqrt{\alpha P} h_{\mathrm{C}} c s[n] + w[n],
		\end{equation}
		where $P$ is the average transmit power at the AP and $w \sim \mathcal{CN}(0,\sigma^2)$ is the additive white Gaussian noise. We also define $\boldsymbol{y} \triangleq \bigl[y[1], \ldots, y[N]\bigr]^T$.

@@

		\begin{remark}
			The main difference between symbiotic radio and conventional MAC is that the primary message also reaches the user from the backscatter link. This characteristic inspires one to first decode the tag message, then model its contribution within the equivalent channel during primary decoding (i.e., unify backscatter decoding and channel training), instead of performing SIC. In such case, the reflection pattern not only embeds the tag message but also adjusts the legacy channel in a controllable manner. Therefore, for a fixed fading block, the primary transmission is able to achieve the ergodic capacity with artificial channel variation created by the backscatter modulation. [Channel over channel, randomness over randomness]
		\end{remark}

		\begin{subsection}{Backscatter Detection}
			To investigate how backscatter modulation potentially benefits the primary transmission, we first decode the tag symbol $c$ in presence of the interference from the primary message $\boldsymbol{s}$. In such case, the detection indeed coincides with that of Ambient Backscatter Communications (AmBC) where the signaling from the ambient source is unknown, and the received signal per symbol block follows the CSCG distribution of $y_m[n] \sim \mathcal{CN}(0,\sigma_m^2)$, where
			\begin{equation}
				\sigma_m^2 \triangleq \lvert h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c_m \rvert^2 P + \sigma^2
			\end{equation}
			can be estimated at the user. For the ease of exposition, we sort $\{\sigma_m^2\}$ in a descending order by bijective mapping $f \colon m \mapsto i$,\footnote{Note that the mapping is not unique and the detection fails when two different constellation points yield the same energy level.} and formulate a sequence $\langle \sigma_i^2 \rangle$ where $\sigma_i^2 \ge \sigma_j^2$ for $i > j$, $i,j \in \mathcal{M}$. Denote $\mathcal{H}_i$ as the hypothesis that the tag transmits $c_i$. Following \cite{Qian2019}, the optimal Maximum-Likelihood (ML) detector boils down to the energy detector, and the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is
			\begin{equation}
				\Lambda_{i, j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{(\sigma_i^2 - \sigma_j^2) z}{\sigma_i^2 \sigma_j^2} \right),
			\end{equation}
			where $f(\boldsymbol{y} \mid \mathcal{H}_i)$, $f(\boldsymbol{y} \mid \mathcal{H}_j)$ denote respectively the conditional probability density function of receiving $\boldsymbol{y}$ under hypothesis $\mathcal{H}_i$ and $\mathcal{H}_j$, and $z \triangleq \lVert y \rVert^2$ is the received signal energy over $N$ symbol blocks. The corresponding decision rule is
			\begin{equation}
				\Lambda_{i, j}(\boldsymbol{y}) \underset{H_j}{\overset{H_i}{\gtrless}} 1 \iff z \underset{H_j}{\overset{H_i}{\gtrless}} T_{i, j},
			\end{equation}
			where the optimal detection threshold is
			\begin{equation}
				T_{i, j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2}.
			\end{equation}
			On top of this, the decision region of hypothesis $\mathcal{H}_i$ can be expressed as
			\begin{equation}
				\mathcal{R}_i \triangleq [T_{i-1, i}, T_{i, i+1}),
			\end{equation}
			where we define $T_{0, 1} \triangleq 0$ and $T_{M, M+1} \triangleq \infty$. On the other hand, the transition probability matrix is
			\begin{equation}
				\boldsymbol{P} =
				\begin{bmatrix}
					p_{1 \mid 1} & \ldots & p_{M \mid 1} \\
					\vdots & \ddots & \vdots \\
					p_{1 \mid M} & \ldots & p_{M \mid M}
				\end{bmatrix},
			\end{equation}
			where $p_{j \mid i}$ denotes the transition probability from channel input state $i$ to output state $j$. It can be derived as
			\begin{equation}
				p_{j \mid i} = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z
				\label{eq:transition_probability}
			\end{equation}
			where $f(z \mid \mathcal{H}_i)$ is the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$. Since $z$ follows chi-squared distribution with $2N$ degrees of freedom, it holds that
			\begin{equation}
				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} \Gamma(N)}
				\label{eq:conditional_pdf}
			\end{equation}
			where $\Gamma(\cdot)$ is the gamma function. Therefore, the transition matrix $\boldsymbol{P}$ can be calculated by substituting \eqref{eq:conditional_pdf} into \eqref{eq:transition_probability}, and the optimal input distribution can be obtained by the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972}.
		\end{subsection}

		\begin{subsection}{Legacy Transmission}
			Once the tag message is successfully recovered, the user combines the backscattered symbol with the cascaded channel to eliminate the uncertainty of the AP-TG-UE path and detects the legacy information. The received signal at symbol block $n$ is essentially
			\begin{equation}
				y[n] = \sqrt{P} (h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c) s[n] + w[n] \triangleq \sqrt{P} h_{\mathrm{E}}(c) s + w[n],
			\end{equation}
			which is reminiscent of IRS-aided point-to-point transmission with an equivalent channel of
			\begin{equation}
				h_{\mathrm{E}}(c) \triangleq h_{\mathrm{D}} + \sqrt{\alpha} h_{\mathrm{C}} c.
			\end{equation}
			For primary transmission, backscatter modulation creates an artificial fast fading within each fading block, and the equivalent CSI is known at the receiver once the backscattered symbol is successfully decoded. Therefore, the ergodic capacity of primary transmission within each symbol block is \cite{Tse2005}
			\begin{equation}
				R_s = \mathbb{E}_c \bigl[ \log_2 ( 1 + \lvert h_{\mathrm{E}}(c) \rvert^2 ) \bigr].
			\end{equation}
			It can be observed that the input distribution of $c$ determines the capacity of both primary and secondary links.
		\end{subsection}
		\label{se:system_model}
	\end{section}

	\begin{section}{Tag Input Distribution}
		To achieve a flexible tradeoff between the backscatter and legacy links, we aims to optimize the probability mass function of the tag input distribution under $M$-PSK modulation. Denote the probability that the tag symbol $c$ takes $c_m$ as $p_m$ and the corresponding probability mass function as $\boldsymbol{p} = [p_1,\ldots,p_M]^T \in \mathbb{R}_+^{M \times 1}$. One possible problem formulation is to maximize the weighted sum of the primary and secondary rates subject to the sum-probability constraint
		\begin{maxi!}
			{\scriptstyle{\boldsymbol{p}}}{\rho R_s + (1 - \rho) R_c}{}{}
			\addConstraint{\sum_{m \in \mathcal{M}} p_m}{=1,}{}
		\end{maxi!}
		where $\rho \in [0, 1]$ is the weight factor to control the backscatter-legacy tradeoff.
	\end{section}
